---
title: "Chapter_12_Tutorial"
author: "Fiona Harrigian"
date: "2025-11-08"
output: html_document
---
```{r packages}
#NEED TO MAKE SURE INCLUDES ALL PACKAGES
library(ggplot2)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Part one is how to create github account, install github for those who don't have it, link repository? copy and paste url from git into R
could we work on different sections and would that create issues with line numbers?

## Discuss Data
Do we need to send invitation to link to repository?
Import CSV into git - all files worked with from day 1 to now

## References
<<<<<<< HEAD
will we have to work on different lines?? will it be possible?

will we have to work on different lines?? will it be possible?

when we are working together, this will appear same line??? one last try
>>>>>>> dbb3cf23349888931e0310ee2ff58305525580f7

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
